Occurrence and transmission potential of asymptomatic and pre-symptomatic SARS-CoV-2 infections: a living systematic review and meta-analysis

### 2021-10-29 Manuscript_draft.Rmd
new run

@@

#create image file
png(file="forest_Q2_2.png", 
    res=300, 
    height=35, width=42, units="cm")
p
dev.off()

>>>>

#create image file

@@

png(file="forest_Q2_2.png", res=300, height=17, width=20, units="cm")
#pdf(file="Figure4.pdf", height=12/2, width=25/3)
p
dev.off()

# png(file="forest_Q2_2.png", 
#     res=300, 
#     height=35, width=42, units="cm")
# p
# dev.off()
